### 2012-05-10 trunk/GUIErrorDetector/paper/evaluation.tex
add the number of explored paths

We manually determined the validity of each warning.
For a known error, we compared the generated report (i.e., the
error-revealing method call chain as Figure~\ref{fig:report} shows) against the
actual error-fixing patch to check whether our tool correctly identified the
erroneous method. For a previously-unknown error, we submitted a new bug
report to its developers, and wrote a test driver to reproduce it.

@@

The third variant uses exhaustive search to find potential errors. This variant
enumerates all non-cyclic paths from all reachable \CodeIn{Thread.start()} nodes
to each UI-accessing node, and then checks whether each
path spawns a new thread and accesses GUI objects without using safe UI methods.
This variant ran out of memory on all subjects, and did not output any real
errors before it terminated.  The number of
non-cyclic paths in a graph is exponential in the graph size, and it 
it is infeasible to enumerate all paths
for a realistic call graph, which often contains thousands of nodes.
%only a very few amount of paths can be enumerated within a practical amount of time.

Given a sound call graph, suppose that there exists some
error-revealing path between an entry node E and a UI-accessing node U\@.  A sound
search strategy is one that reports some error-revealing path between
E and U, while an unsound strategy might report a non-error-revealing
path between the nodes (Figure~\ref{fig:ex} shows an example).
Exhaustive search is sound because it does not
miss any possible (non-cyclic) paths.  However, it is impractical.
BFS and DFS are unsound because they visit
every node, but do not traverse every \emph{path} path to visit that node.
Using BFS or DFS can be viewed as a heuristic filtering
step, akin to the filters of Section~\ref{sec:heuristic}.
% The heuristics of Section~\ref{sec:heuristic} are
%more effective at retaining real errors than the search variants.
%Given a sound call graph, exhaustive search is sound because it does not
%miss any possible errors.  However, it is impractical.  Compared to
%exhaustive search, using BFS or DFS can be viewed as a heuristic filtering
%step, akin to the filters of Section~\ref{sec:heuristic}.
%The heuristics of Section~\ref{sec:heuristic} are
%more effective at retaining real errors than the search variants.

@@

\noindent \textbf{\textit{Limitations.}}
Our technique is limited in three aspects. First, it only considers
non-UI threads that are spawned by the UI-thread after the GUI
is initialized, and ignores other possible non-UI threads (quite unusual)
that are created during the pre-initialization GUI work. One way
to remedy this limitation is to design an analysis to identify
those non-UI threads created before a GUI is launched.
Second, like many bug-finding techniques, our technique
is neither sound nor complete. It may miss true positives due
to the graph search strategy, and it never reports cyclic paths.  It may
issue false positives due to the conservative nature of
a static analysis. Designing better call graph construction algorithms,
graph search strategies, and filtering heuristics may alleviate this limitation.
Third, our tool cannot compute call relationships
for inter-process communication between components. It also
requires users to manually add annotations to characterize
call relationships that involve native methods. This limitation
may lead to false negatives. Investigating the false negative
rate is ongoing work.

>>>>

We manually determined the validity of each warning.
For a known error, we compared the generated report (i.e., the
error-revealing method call chain as Figure~\ref{fig:report} shows) against the
actual error-fixing patch to check whether our tool correctly identified the
erroneous method. For a previously-unknown error, we submitted a new bug
report to its developers, and wrote a test driver to reproduce it.
%wrote a test driver to

@@

The third variant uses exhaustive search to find potential errors. This variant
enumerates all non-cyclic paths from all reachable \CodeIn{Thread.start()} nodes
to each UI-accessing node, and then checks whether each
path spawns a new thread and accesses GUI objects without using safe UI methods.
However, the number of non-cyclic paths in a graph is exponential in the graph size,
and it is infeasible for this variant to enumerate all paths for a realistic
call graph, which often contains thousands of
nodes (e.g., $2^{1000}$ $\approx$ 1.07$\times$$10^{301}$). In our experiment,
we ran this variant on each subject for 1 hour, it explored 1.6$\times$$10^9$ paths on average, but did not
output any real errors before it terminated.

%for a realistic call graph consisting of thousands
%of nodes,

%only a very few amount of paths can be enumerated within a practical amount of time.

Given a sound call graph, suppose that there exists some
error-revealing path between an entry node E and a UI-accessing node U\@.  A sound
search strategy is one that reports some error-revealing path between
E and U, while an unsound strategy might report a non-error-revealing
path between the nodes (Figure~\ref{fig:ex} shows an example).
Exhaustive search is sound because it does not
miss any possible (non-cyclic) paths.  However, it is impractical.
BFS and DFS are unsound because they visit
every node, but do not traverse every path to visit that node.
Using BFS or DFS can be viewed as a heuristic filtering
step, akin to the filters of Section~\ref{sec:heuristic}.
% The heuristics of Section~\ref{sec:heuristic} are
%more effective at retaining real errors than the search variants.
%Given a sound call graph, exhaustive search is sound because it does not
%miss any possible errors.  However, it is impractical.  Compared to
%exhaustive search, using BFS or DFS can be viewed as a heuristic filtering
%step, akin to the filters of Section~\ref{sec:heuristic}.
%The heuristics of Section~\ref{sec:heuristic} are
%more effective at retaining real errors than the search variants.

@@

\noindent \textbf{\textit{Limitations.}}
Our technique is limited in three aspects. First, it only considers
non-UI threads that are spawned by the UI-thread after the GUI
is initialized, and ignores other possible non-UI threads (quite unusual)
that are created during the pre-initialization GUI work. One way
to remedy this limitation is to design an analysis to identify
those non-UI threads created before a GUI is launched.
Second, like many bug-finding techniques, our technique
is neither sound nor complete. It may issue false positives
due to the conservative nature of a static analysis.
It may miss true positives due to the graph search strategy,
and it never reports cyclic paths. Furthermore, for the
sake of scalability, our tool implementation uses the default
configuration of WALA and ignores part of the AWT library. Thus,
it missed one error in S3dropbox which can be found by using a different
technique~\cite{JSR308-webpage-201110}.
Designing better call graph construction algorithms,
graph search strategies, and filtering heuristics may alleviate this limitation.
Third, our tool cannot compute call relationships
for inter-process communication between components. It also
requires users to manually add annotations to characterize
call relationships that involve native methods. This limitation
may lead to false negatives. Investigating the false negative
rate is ongoing work.
